---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Graph

### Homework

You are tasked with reproducing the following figure:

```{r plot, echo = F, message = F, warning=F, fig.height=7, fig.width=8}
library(tidyverse)
library(carData)
library(ggthemes)

UN98 %>% 
  ggplot(aes(lifeFemale, GDPperCapita, col = economicActivityFemale)) + 
  geom_point() + scale_y_log10(labels = scales::dollar_format()) + 
  facet_grid(.~region) + 
  geom_smooth(se = F, method = "lm", colour = "firebrick4") + 
  scale_color_gradient(low = "yellow", high = "darkred") + 
  theme_wsj() +
  labs(title = "Per capita GDP as a function\nof Female Life Expectancy", caption = "@Data from carData", colour = "Female Economic Activity") + 
  theme(strip.text = element_text(size = 16, family = "Ink Free"))
```

```{r gdp-lifeExp, exercise=TRUE, warning = F, message = F, fig.width=8, fig.height=7}

```

## Procedure

- You'll need the _tidyverse_ library, the _carData_ library (install from CRAN by _install.packages("carData")_), the _scales_ package, the _showtext_ package, and the _ggthemes_ library (install from CRAN by _install.packages("ggthemes")_) 
- The dataset is called _UN98_ from _carData_.
- There are three aesthetics; for x = _lifeFemale_, y = _GDPperCapita_, and colour = _economicActivityFemale_
- Add the graph title, the legend title, and add a caption
- The y axis should be plotted on a log scale with the labels set to _dollar()_ from the _scales_ package
- Facet by _region_, use either _facet_grid()_ or _facet_wrap()_ as appropriate
- Add a _geom_smooth()_ with _method = "lm"_ and _se = F_
- Add an appropriate colour scale for the _economicActivityFemale_ aesthetic.
- Set the theme for the plot with the _theme_wsj_ theme from the _ggthemes_ package (wsj copies the theme from the _Wall Street Journal_).
- install some handwriting font with _font_add_google()_, don't forget to make it available with _showtext_auto()_. Use _theme(strip.text = element_text(.......))_ to print the continent names in this font. Make sure you do this after _theme_wsj()_ or else it gets overwritten.
- As before, add something extra that enhances the image.
