---
title: "Lunchtime Challenge"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Graph

### You are tasked with reproducing the following figure:

```{r plot, echo = F, message = F, warning=F, fig.height=6}
library(tidyverse)
library(dslabs)

death_prob %>% 
  ggplot(aes(age, prob, col = sex)) + 
  geom_point() + 
  scale_y_log10() + 
  labs(title = "Probability of Death within 1 Year by Age and Sex\nin the United States in 2015", x = "Age in Years", y = "Probability of Death", caption = "@Data from DSLabs")
```


```{r lunchtime, exercise=TRUE}

```

## Procedure

- You'll need the _tidyverse_ library and the _dslabs_ library (install from CRAN by _install.packages("dslabs")_)
- Get the dataset using _data("death_prob")_
- You'll need to call ggplot setting _data = death_prob_
- There are three aesthetics; for _age_, _prob_, and _sex_
- Add the graph title, the axes labels, and add a caption
- The y axis should be plotted on a log scale (using *scale_y_log10*)
- There is also extra kudos for improving the figure with your own ideas
